Measuring precise radial velocities and cross-correlation function line-profile variations using a Skew Normal density\thanks{Based on observations collected at the La Silla Parana Observatory, ESO (Chile), with the HARPS spectrograph at the 3.6-m telescope.}

### 2018-06-25 manuscript.tex
Add files via upload
just added a small comment

A test was carried out to see if some RV estimates were better at finding planets in RV data affected by observed stellar signals. 
When using the new correction proposed in this paper to mitigate the effect from stellar activity and when assessing planetary detection based on a periodogram analysis, we find very similar detection limits for the three RV estimators presented in this paper. 
\jessi{Maybe to try another test to see if the proposed correction is helpful, the detection-limit test could be carried out with the usual correction and we can see if it does not performa s well.}
\umberto{waiting for new results with usual correction.}
Therefore it seems that any of the RV estimate can be used to search for planetary signals.

@@

We are grateful to all technical and scientific collaborators of the HARPS Consortium, ESO Headquarters and ESO La Silla who have contributed with their extraordinary passion and valuable work to the success of the HARPS project.
XD is grateful to The Branco Weiss Fellowship--Society in Science for its financial support.

%-----------------------------------------------------------------------------------------------------------------------------------------------
%\section{Appendix}
\appendix
\section{Appendix} \label{appendix}

>>>>

A test was carried out to see if some RV estimates were better at finding planets in RV data affected by observed stellar signals. 
When using the new correction proposed in this paper to mitigate the effect from stellar activity and when assessing planetary detection based on a periodogram analysis, we find very similar detection limits for the three RV estimators presented in this paper. 
\umberto{trying to understand why we get better results for P=20 days when using the usual correction}
Therefore it seems that any of the RV estimate can be used to search for planetary signals.

@@

We are grateful to all technical and scientific collaborators of the HARPS Consortium, ESO Headquarters and ESO La Silla who have contributed with their extraordinary passion and valuable work to the success of the HARPS project.
XD is grateful to The Branco Weiss Fellowship--Society in Science for its financial support.
JCK was partially supported by the National Science Foundation under Grant AST 1616086 and by the National Aeronautics and Space Administration under grant 80NSSC18K0443.
US was partially supported by Fondazione CARIPARO. \umberto{check if there is a code or something}
%-----------------------------------------------------------------------------------------------------------------------------------------------
%\section{Appendix}
\appendix
\section{Appendix} \label{appendix}
